Dominance Regions for Rank Two Cluster Algebras

### 2022-04-08 dominance_regions.tex
Proof of Theorem 1

  \begin{lemma}
    We have
    \[\lim_{i\to\infty} \frac{-u_i^-}{u_{i-1}^+}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1}^-}{u_i^+}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}.\]
    Moreover, each of these sequences is monotonic.
  \end{lemma}
  \begin{proof}
    For any $i\ge 1$, we have
    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
    It follows that
    \[\lim_{i\to\infty} \frac{-u_i^-}{u_{i-1}^+} = \lim_{i\to\infty} \left( \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
    which is equivalent to the desired expression.
    Similarly, 
    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
    so that
    \[\lim_{i\to\infty} \frac{-u_{i-1}^-}{u_i^+} = \lim_{i\to\infty} \left( \frac{-2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
    which is again equivalent to the desired expression.

@@

  Similar arguments with the inequalities \eqref{ieq4}-\eqref{ieq6} lead to the remaining inequalities determining the boundary of $\cP(\lambda)$:
  \[ 0 \le (\mu_0-\lambda_0)+\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1);\]
  \[ b\lambda_1 \le (\mu_0-\lambda_0)-\frac{bc+\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1);\]
  \[ c\lambda_0+b\frac{bc-\sqrt{bc(bc-4)}}{2b}\lambda_1 \le -\frac{bc+\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1).\]

  %\begin{lemma}
  %  For $k \le -1$ and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
  %  \begin{align}
  %    \label{ineq:1} u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
  %    \label{ineq:2} u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
  %    \label{ineq:3} u_k^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
  %    \label{ineq:4} -u_{k+2}^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1.
  %  \end{align}
  %  
  %  given as in the figure below:
  %  \[
  %    \begin{tikzpicture}
  %      \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
  %      \draw[-] (-8,0) -- (5,0);
  %      \draw[-] (0,-5) -- (0,5);
  %      %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
  %      \draw[dashed] (0,0) -- (5,-2.113);
  %      \draw[dashed] (0,0) -- (3.17,-5);
  %      \node at (1,-0.9) {$\cI$};
  %      \draw[fill=black] (3.5,-3) circle (2pt);
  %      \node[right] at (3.5,-3) {$\lambda$};
  %      \draw[->,thick] (3.5,-3) -- (47/10,-5);
  %      \draw[-,thick] (3.5,-3) -- (0,26/10);
  %      \draw[-,thick] (0,26/10) -- (-26/4,0);
  %      \draw[->,thick] (-26/4,0) -- (-16/4,-5);
  %      \node at (4.5,-4) {\eqref{ineq:1}};
  %      \node at (2.34,-0.5) {\eqref{ineq:2}};
  %      \node at (-3,1.75) {\eqref{ineq:3}};
  %      \node at (-5.36,-3) {\eqref{ineq:4}};
  %    \end{tikzpicture}
  %  \]
  %\end{lemma}
  %\begin{proof}
  %  Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.

>>>>

  \begin{lemma}
    We have
    \[\lim_{i\to\infty} \frac{-u_i^-}{u_{i-1}^+}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1}^-}{u_i^+}=\frac{-bc+\sqrt{bc(bc-4)}}{2b};\]
    \[\lim_{i\to-\infty} \frac{-u_i^-}{u_{i-1}^+}=\frac{-bc+\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to-\infty} \frac{-u_{i-1}^-}{u_i^+}=\frac{-bc-\sqrt{bc(bc-4)}}{2b}.\]
    Moreover, each of these sequences is monotonic.
  \end{lemma}
  \begin{proof}
    For any $i\ne1$, we have
    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
    It follows that
    \[\lim_{i\to\infty} \frac{-u_i^-}{u_{i-1}^+} = \lim_{i\to\infty} \left( \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
    which is equivalent to the desired expression.
    Similarly, for $i\ne0$ we have
    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
    so that
    \[\lim_{i\to\infty} \frac{-u_{i-1}^-}{u_i^+} = \lim_{i\to\infty} \left( \frac{-2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
    which is again equivalent to the desired expression.
    This proves the claim for $i\to\infty$, the cases $i\to-\infty$ follow from these using $u_{-i}^\varepsilon=-u_i^\varepsilon$.

@@

  Similar arguments with the inequalities \eqref{ieq4}-\eqref{ieq6} lead to the remaining inequalities determining the boundary of $\cP(\lambda)$:
  \[ 0 \le \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1);\]
  \[ b\lambda_1 \le (\mu_0-\lambda_0)-\frac{bc-\sqrt{bc(bc-4)}}{2c}(\mu_1-\lambda_1) \le 0;\]
  \[ \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)+(\mu_1-\lambda_1) \le -c\lambda_0-\frac{bc+\sqrt{bc(bc-4)}}{2b}b\lambda_1.\]

  This completes the proof of Theorem~\ref{th:dominance inequalities}.
  %\begin{lemma}
  %  For $k \le -1$ and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
  %  \begin{align}
  %    \label{ineq:1} u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
  %    \label{ineq:2} u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
  %    \label{ineq:3} u_k^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
  %    \label{ineq:4} -u_{k+2}^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1.
  %  \end{align}
  %  
  %  given as in the figure below:
  %  \[
  %    \begin{tikzpicture}
  %      \filldraw[color=lightgray!30] (47/10,-5) --(3.5,-3) -- (0,26/10) -- (-26/4,0) -- (-16/4,-5);
  %      \draw[-] (-8,0) -- (5,0);
  %      \draw[-] (0,-5) -- (0,5);
  %      %\filldraw[color=lightgray!30] (0,0) -- (5,-2.113) -- (5,-5) -- (3.17,-5) -- (0,0);
  %      \draw[dashed] (0,0) -- (5,-2.113);
  %      \draw[dashed] (0,0) -- (3.17,-5);
  %      \node at (1,-0.9) {$\cI$};
  %      \draw[fill=black] (3.5,-3) circle (2pt);
  %      \node[right] at (3.5,-3) {$\lambda$};
  %      \draw[->,thick] (3.5,-3) -- (47/10,-5);
  %      \draw[-,thick] (3.5,-3) -- (0,26/10);
  %      \draw[-,thick] (0,26/10) -- (-26/4,0);
  %      \draw[->,thick] (-26/4,0) -- (-16/4,-5);
  %      \node at (4.5,-4) {\eqref{ineq:1}};
  %      \node at (2.34,-0.5) {\eqref{ineq:2}};
  %      \node at (-3,1.75) {\eqref{ineq:3}};
  %      \node at (-5.36,-3) {\eqref{ineq:4}};
  %    \end{tikzpicture}
  %  \]
  %\end{lemma}
  %\begin{proof}
  %  Following Lemma~\ref{le:imaginary transformations}, we consider even and odd sequences of mutations separately.
